Paper 3 - Tables

### 2023-08-01 docs/causal_roadmap.qmd
Trying to use targets to compile documents for paper.

---
title: "Paper 3 - Causal Roadmap"
keywords:
  - Causal Inference
  - Epidemiology
  - Triangulation
  - Modified Treatment Policy
  - Mendelian Randomization
  - Metabolomics
  - Endocrine Disrupting Chemicals
  - Neurodevelopment
  - Neurobehavior
metadata-files:
  - ../../../all_phd/authors.yml
format:
  pdf:
    pdf-engine: pdflatex
    number-sections: true
    toc: false
    margin-left: 15mm
    margin-right: 15mm
    margin-bottom: 20mm
    margin-top: 15mm
    include-in-header:
      text: |
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}
bibliography: ../../../PhD.bib
link-citations: true
linkcolor: blue
execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
filters:
  - acronyms
  - authors-block
acronyms:
  fromfile: ../../../all_phd/acronyms.yml
  insert_links: false
  insert_loa: false
  sorting: alphabetical
---

@@

```{r}
#| include: false

here::i_am("causal_roadmap.qmd")
source("../../../all_phd/info_phd.R")
source("../../../all_phd/triangulation_methods.R")
infos <- info_phd()
methods <- describe_triangulation_methods()

library(tidyverse)
```

>>>>

---
title: "Paper 3 - Causal Roadmap"
keywords:
  - Causal Inference
  - Epidemiology
  - Triangulation
  - Modified Treatment Policy
  - Mendelian Randomization
  - Metabolomics
  - Endocrine Disrupting Chemicals
  - Neurodevelopment
  - Neurobehavior
metadata-files:
  - ../../../all_phd/authors.yml

format:
  pdf:
    pdf-engine: pdflatex
    number-sections: true
    toc: false
    margin-left: 15mm
    margin-right: 15mm
    margin-bottom: 20mm
    margin-top: 15mm
    include-in-header:
      text: |
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}

bibliography: ../../../PhD.bib
link-citations: true
linkcolor: blue

execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console

filters:
  - ../../../all_phd/_extensions/acronyms/parse-acronyms.lua
  - ../../../all_phd/_extensions/authors-block/authors-block.lua
acronyms:
  fromfile: ../../../all_phd/acronyms.yml
  insert_links: false
  insert_loa: false
  sorting: alphabetical
---

@@

```{r}
#| include: false
source("../../../all_phd/info_phd.R")
source("../../../all_phd/triangulation_methods.R")

here::i_am("causal_roadmap.qmd")
infos <- info_phd()
methods <- describe_triangulation_methods()
```

### 2023-08-01 output/paper/figures.qmd
Trying to use targets to compile documents for paper.

---
title: "Paper 3 - Figures"
format:
  pdf:
    pdf-engine: pdflatex
    toc: false
    include-in-header:
      text: |
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}
link-citations: true
linkcolor: blue
execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
project:
  execute_dir: project
---

```{r}
#| include: false
here::i_am("figures.qmd")

library(tidyverse)
```

>>>>

---
title: "Paper 3 - Figures"

format:
  pdf:
    pdf-engine: pdflatex
    toc: false
    include-in-header:
      text: |
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}

link-citations: true
linkcolor: blue

execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
---

### 2023-08-01 output/paper/manuscript.qmd
Trying to use targets to compile documents for paper.

---
metadata-files:
  - ../../../../all_phd/authors.yml
format:
  pdf:
    pdf-engine: pdflatex
    number-sections: true
    toc: false
    include-in-header:
      text: |
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}
bibliography: ../../../../PhD.bib
link-citations: true
linkcolor: blue
execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
filters:
  - ../../../../all_phd/_extensions/acronyms/parse-acronyms.lua
  - ../../../../all_phd/_extensions/authors-block/authors-block.lua
acronyms:
  fromfile: ../../../../all_phd/acronyms.yml
  insert_links: false
  insert_loa: false
  sorting: alphabetical
abstract: |
 **Background**

@@

```{r}
#| include: false

here::i_am("manuscript.qmd")
source("../../../../all_phd/info_phd.R")
infos <- info_phd()
```

---
title: "`r infos$paper3$title`"
---

<!-- ####################################################################### -->
<!-- INTRODUCTION -->
# Introduction {#intro}
```{r}
#| child: sections/introduction.qmd
```
<!-- ####################################################################### -->

<!-- ####################################################################### -->
<!-- METHODS -->
# Methods {#methods}
```{r}
#| child: sections/methods.qmd
```
<!-- ####################################################################### -->

<!-- ####################################################################### -->
<!-- RESULTS -->
# Results {#res}
```{r}
#| child: sections/results.qmd
```
<!-- ####################################################################### -->

<!-- ####################################################################### -->
<!-- DISCUSSION -->
# Discussion {#discussion}
```{r}
#| child: sections/discussion.qmd
```
<!-- ####################################################################### -->

@@

# References

>>>>

---
metadata-files:
  - ../../../../all_phd/authors.yml

format:
  pdf:
    pdf-engine: xelatex
    number-sections: true
    toc: false
    include-in-header:
      text: |
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}

bibliography: ../../../../PhD.bib
link-citations: true
linkcolor: blue

execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console

filters:
  - ../../../../all_phd/_extensions/acronyms/parse-acronyms.lua
  - ../../../../all_phd/_extensions/authors-block/authors-block.lua
acronyms:
  fromfile: ../../../../all_phd/acronyms.yml
  insert_links: false
  insert_loa: false
  sorting: alphabetical

abstract: |
 **Background**

@@

---
title: "Some Title"
---

<!-- ####################################################################### -->
# Introduction {#intro}
```{r}
#| child: output/paper/sections/introduction.qmd
```
<!-- ####################################################################### -->

<!-- ####################################################################### -->
# Methods {#methods}
```{r}
#| child: output/paper/sections/methods.qmd
```
<!-- ####################################################################### -->

<!-- ####################################################################### -->
# Results {#res}
```{r}
#| child: output/paper/sections/results.qmd
```
<!-- ####################################################################### -->

<!-- ####################################################################### -->
# Discussion {#discussion}
```{r}
#| child: output/paper/sections/discussion.qmd
```
<!-- ####################################################################### -->

@@

<!-- ####################################################################### -->
# References {.unnumbered}
<!-- ####################################################################### -->

::: {#refs}
:::

### 2023-08-01 output/paper/tables.qmd
Trying to use targets to compile documents for paper.

---
title: "Paper 3 - Tables"
format:
  docx:
    reference-doc: reference_document.docx
link-citations: true
linkcolor: blue
execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
project:
  execute_dir: project
---

```{r}
#| include: false
here::i_am("tables.qmd")

library(tidyverse)
```

@@

<!-- ####################################################################### -->
# Exposures
<!-- ####################################################################### -->
```{r}
#| label: tbl-chem-info
#| tbl-cap: Information about the non-persistent EDCs.
edcs_info <- myphd::edcs_information() %>%
  dplyr::select(-c(chem_id, smiles))
gt::gt(edcs_info, groupname_col = "class") %>%
  gt::cols_label(
    full_name = "Compound", 
    short_name = "Symbol", 
    #smiles = "SMILES", 
    pubchem_cid = "PubChem CID", 
    ctd_id = "CTD ID", 
    exposome_explorer_id = "Exposome Explore ID", 
    parental_compound = "Parental compound"
  ) %>%
  gt::tab_style(
    locations = gt::cells_column_labels(columns = everything()), 
    style = list(
      gt::cell_borders(sides = "bottom", weight = gt::px(3)), 
      gt::cell_text(weight = "bold")
    )
  ) %>%
  gt::tab_style(
    locations = gt::cells_row_groups(group = everything()), 
    style = list(gt::cell_text(weight = "bold"))
  )
```

>>>>

---
title: "Paper 3 - Tables"

format:
  docx:
    reference-doc: reference_document.docx

link-citations: true
linkcolor: blue

execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
---

@@

<!-- ####################################################################### -->
# Exposures
<!-- ####################################################################### -->
```{r}
#| label: tbl-chem-info
#| tbl-cap: Information about the non-persistent EDCs.
edcs_info <- myphd::edcs_information() |>
  dplyr::select(-c(chem_id, smiles))
gt::gt(edcs_info, groupname_col = "class") |>
  gt::cols_label(
    full_name = "Compound", 
    short_name = "Symbol", 
    pubchem_cid = "PubChem CID", 
    ctd_id = "CTD ID", 
    exposome_explorer_id = "Exposome Explore ID", 
    parental_compound = "Parental compound"
  ) |>
  gt::tab_style(
    locations = gt::cells_column_labels(columns = everything()), 
    style = list(
      gt::cell_borders(sides = "bottom", weight = gt::px(3)), 
      gt::cell_text(weight = "bold")
    )
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()), 
    style = list(gt::cell_text(weight = "bold"))
  )
```
